Concurrent Programming with CXL

### 2020-06-24 book/paper.tex
Now most code can run as is.

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWbusy.cxl}
\end{code}
\caption{[RWbusy.cxl] Busy-Waiting Reader/Writer Lock implementation.}
\label{fig:rwbusy}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWbusytest.cxl}
\end{code}
\caption{[RWbusytest.cxl] Test code for Figure~\ref{fig:rwbusy}.}
\label{fig:rwbusytest}
\end{figure}

@@

Figure~\ref{fig:rw2lock} presents a reader/writer lock implementation
that does not busy-wait.
It uses two ordinary locks: \texttt{rwlock} is used by both readers and writers,
while \texttt{rlock} is only used by readers.
\texttt{rwlock} is held either when readers are at label \texttt{@rcs}
or when a writer is at label \texttt{@wcs}.
\texttt{rlock} is used to protect the \texttt{nreaders} variable that
counts the number of readers in the critical section.

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RW.cxl}
\end{code}
\caption{[RW.cxl] Busy-Waiting Reader/Writer Lock implementation.}
\label{fig:rwbusy}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWtest.cxl}
\end{code}
\caption{[RWtest.cxl] Test code for Figure~\ref{fig:rwbusy}.}
\label{fig:rwbusytest}
\end{figure}

@@

Figure~\ref{fig:rw2lock} presents a reader/writer lock implementation
that does not busy-wait.
You can test the code by running \texttt{cxl -m RW=RWlock RWtest}.
It uses two ordinary locks: \texttt{rwlock} is used by both readers and writers,
while \texttt{rlock} is only used by readers.
\texttt{rwlock} is held either when readers are at label \texttt{@rcs}
or when a writer is at label \texttt{@wcs}.
\texttt{rlock} is used to protect the \texttt{nreaders} variable that
counts the number of readers in the critical section.
